Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-12-05 presentations/illustrations/presentation-illustrations.tex
finished register file part for attack 1.

    % Caller 
    \actsf{(0,2.5)}{(6,5)}{caller stack frame} 
    \begin{onlyenv}<+>
      \capbrace[sp1]{(6.5,2.5)}{(6.5,16)}
      \draw node[right=0cm of sp1] { stack pointer };
      \draw (r1) edge[->,red,bend left] (sp1);
    \end{onlyenv}

    % Split the stack pointer
    \begin{onlyenv}<+>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw (r2) edge[->,red,bend left] (sp2);
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,5) -- (6.5,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw (r1) edge[->,red,bend left] (usp);
      \draw node[right=0cm of usp] { stack pointer };
      \draw node[right=0cm of sp2] { private stack pointer };
    \end{onlyenv}

    % Callee called
    \begin{onlyenv}<+>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw (r2) edge[->,red,bend left] (sp2);
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,5) -- (6.5,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw (r1) edge[->,red,bend left] (usp);
      \draw node[right=0cm of usp] { stack pointer };
      \draw node[fill=gray,opacity=0.5, right=0cm of sp2] { return data pointer };
      \inactsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \actadv{(0,5)}{(6,8)}{callee stack frame}
    \end{onlyenv}

@@

    % Callee stores stack pointer
    \begin{onlyenv}<+->
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (8,5) -- (8,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw (14,10.25) edge[->,red,thick,bend right] (usp);
      \draw (16,15) node {heap memory};
    \end{onlyenv}
    \begin{onlyenv}<.>
      \draw[fill=white] (14,10) rectangle node[color=red] {\scriptsize old sp} (18,10.5);
      \draw node[right=0cm of usp] { stack pointer };
      \inactsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \actadv{(0,5)}{(6,8)}{callee stack frame}
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw node[fill=gray!50, right=0cm of sp2] { return data pointer };
    \end{onlyenv}

>>>>

    % Caller 
    \actsf{(0,2.5)}{(6,5)}{caller stack frame} 
    \begin{onlyenv}<+>
      \capbrace[sp1]{(6.5,2.5)}{(6.5,16)}
      \draw node[right=0cm of sp1] { stack pointer };
      \draw (r1) edge[->,red,thick,bend left] (sp1);
    \end{onlyenv}

    % Split the stack pointer
    \begin{onlyenv}<+>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw (r2) edge[->,red,thick,bend left] (sp2);
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,5) -- (6.5,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw (r1) edge[->,red,thick,bend left] (usp);
      \draw node[right=0cm of usp] { stack pointer };
      \draw node[right=0cm of sp2] { private stack pointer };
    \end{onlyenv}

    % Callee called
    \begin{onlyenv}<+>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,5) -- (6.5,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw (r1) edge[->,red,bend left] (usp);
      \draw node[right=0cm of usp] { stack pointer };

      \draw node[fill=gray,opacity=0.5, right=0cm of sp2] { \phantom{return data pointer} };
      \draw node[right=0cm of sp2] { return data pointer };
      \inactsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \actadv{(0,5)}{(6,8)}{callee stack frame}
    \end{onlyenv}
    \draw<.-> (r2) edge[->,red,bend left] (sp2);

@@

    % Callee stores stack pointer
    \begin{onlyenv}<+->
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (8,5) -- (8,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw (14,10.25) edge[->,red,thick,bend right] (usp);
      \draw (16,15) node {heap memory};
    \end{onlyenv}

    \begin{onlyenv}<.>
      \draw[fill=white] (14,10) rectangle node[color=red] {\scriptsize old sp} (18,10.5);
      \draw node[right=0cm of usp] { stack pointer };
      \inactsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \actadv{(0,5)}{(6,8)}{callee stack frame}
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw node[fill=gray,opacity=0.5, right=0cm of sp2] { \phantom{return data pointer} };
      \draw node[right=0cm of sp2] { return data pointer };
    \end{onlyenv}
